---
title: "Ford_Ka_Cluster"
author: "Donny"
date: "12/02/2022"
output: 
 pdf_document:
    latex_engine: xelatex
    toc: yes
    number_sections: yes
    highlight: haddock
  html_document: 
    toc: yes
    highlight: haddock
    number_sections: yes
 editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Prepare

1. Load Packages and Data

## Save the working project into working directory
```{r}
setwd("~/Desktop/MFRE_2022/Winter_2022/FRE_518/Ford_Ka_Cluster")
```

## Load relevant packages with pacman
```{r}
pacman::p_load(tidyverse, ggplot2, here, readxl, janitor, modelsummary, kableExtra, cluster, estimatr)
```

## Load required datasets from Excel Worksheet
```{r}
demographic <- read_excel("./Ford.xls", sheet = "Demographic Data", skip = 6, col_names = TRUE)

demographic <- clean_names(demographic, "upper_camel") 
```

```{r}
demographic <- demographic %>%
        rename(FirstTimePurchase = X1StTimePurchase)
```

```{r}
psychographic <- read_excel("./Ford.xls", sheet = "Psychographic Data", skip = 6, col_names = TRUE)

psychographic <- clean_names(psychographic, "upper_camel")
```

## Use "left_join()" to join the two dataframes together
```{r}
joined_data <- left_join(demographic, psychographic, by = "RespondentNumber")
```

2. Data Cleaning

## Use mutate() and factor() to change the following variables to factors: PreferenceGroup, Gender, MaritalStatus, FirstTimePurchase, AgeCategory, ChildrenCategory, IncomeCategory. See here for some examples.

```{r}
joined_data <- joined_data %>%
        mutate(PreferenceGroup = factor(PreferenceGroup)) %>%
        mutate(Gender = factor(Gender)) %>%
        mutate(MaritalStatus = factor(MaritalStatus)) %>%
        mutate(FirstTimePurchase = factor(FirstTimePurchase)) %>%
        mutate(AgeCategory = factor(AgeCategory)) %>%
        mutate(ChildrenCategory = factor(ChildrenCategory)) %>%
        mutate(IncomeCategory = factor(IncomeCategory))
```

3. Crosstabs Analysis

```{r}
joined_data_1 <- joined_data %>%
        filter(PreferenceGroup != 3) %>%
        droplevels() %>%
        select(PreferenceGroup, Gender, MaritalStatus, FirstTimePurchase, AgeCategory, ChildrenCategory, IncomeCategory)
        
```

```{r}
joined_data_1$PreferenceGroup <- factor(joined_data_1$PreferenceGroup, labels = c("Ka Chooser", "Ka Non-Chooser"))
joined_data_1$Gender <- factor(joined_data_1$Gender, labels = c("Male", "Female"))
joined_data_1$MaritalStatus <- factor(joined_data_1$MaritalStatus, labels = c("Married", "Living Together", "Single"))
joined_data_1$FirstTimePurchase <- factor(joined_data_1$FirstTimePurchase, labels = c("yes", "no"))
joined_data_1$AgeCategory <- factor(joined_data_1$AgeCategory, labels = c("<25", "25 - 29", "30 - 34", "35 - 39", "40 - 44", ">44"))
joined_data_1$ChildrenCategory <- factor(joined_data_1$ChildrenCategory, labels = c("0", "1", ">1"))
joined_data_1$IncomeCategory <- factor(joined_data_1$IncomeCategory, labels = c("<100K", "100K - 150K", "150K - 200K", "200K - 250K", "250K - 300K", ">300K"))
```


```{r}
library(kableExtra)

datasummary_balance(~PreferenceGroup, 
                    data = joined_data_1,
                    output = 'kableExtra') 
        
 
```

4. Clustering Analysis

```{r}
ford_psyc <- psychographic %>%
        select(- RespondentNumber)

set.seed(2025)

Cluster4 <- kmeans(ford_psyc, centers = 4, iter.max = 10, nstart = 25)

Cluster4

ford_psyc$cluster <- Cluster4$cluster

```

5. Crosstabs of 4-cluster analysis

```{r}
ford_psyc_1 <- ford_psyc %>%
        rename_with(~psyc_q$Statement, starts_with("q"))
```

```{r}
datasummary_balance(~cluster, 
                    data = ford_psyc_1,
                    output = 'kableExtra')
```

```{r}
joined_data_again <- cbind(demographic, ford_psyc_1)
datasummary_crosstab(cluster ~ Gender, data = joined_data_again)
```









